Predictive Regressions with Persistent Regressors

### 2019-09-12 paper.tex
clean up

Campbell and Yogo (2006) use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of non-stationarity can be rejected. Elliott and Stock (1994) show, however, that this does not guarantee valid inference via the t-statistic. Instead, Campbell and Yogo (2006) use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of Stock (1991). $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold for $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by Campbell and Yogo (2006), who use the DF-GLS test statistic proposed by Elliott et al. (1996) to construct the confidence interval for $c$. The application accompanying uses the closest tabulated values to the estimated values without interpolating.

@@

As argued by Phillips (2014), the Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrate as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

%Jacquier et al. (2004), however, show that this assumption might be too restrictive to adequately model the dynamics in reality. In the following I will show finite sample rejection rates when the ... modeled as a BEKK GARCH(1,1) process approaches nonstationarity.
It is therefore interesting to observe the behavior of the Bonferroni Q-test if innovations are modeled by a generalized autoregressive conditional heteroskedasticity [GARCH] process that approaches covariance non-stationarity. If the regressor is a valuation ratio, it seems sensible that there is a more or less stable correlation between the regressor and stock returns. A multivariate GARCH model that allows such a restriction is the Constant Conditional Correlations GARCH  [CCC-GARCH] model of Bollerslev (1990). Let $ \boldsymbol{z_{t}}$ be a bivariate standard normal random variable, i.e., $ \boldsymbol{z}_{t} \stackrel{i i d}{\sim} \mathrm{N}\left(\mathbf{0}, \boldsymbol{I}_{2}\right)$. Then the innovations are modeled as 

@@

\section{Empirical Results}

@@

Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of Campbell and Yogo (2006). The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by Campbell and Yogo (2006).  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. Thus the different selection is likely due to rounding errors. 

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor. The null hypothesis of no predictability can be rejected at the 10\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively, using data from Campbell and Yogo (2006). Based on the extended dataset from Amid Goyal, only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First, returns in the extended dataset are of the S\&P500 instead of the CRSP value-weighted index. Also, due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since Campbell and Yogo (2006) use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos}, predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  

@@

Since the original publication of Campbell and Yogo (2006) a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 10\% significance level for any of the regressors and sampling frequencies considered. 
\begin{table}[h]
\small
\setlength\tabcolsep{5.3pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

The Bonferroni Q-test is a asymptotically valid test of predictability if the regressor's largest autoregressive root is local-to-unity and the bivariate Gaussian innovations of regressor and regressand are highly correlated. It has been shown in the original work by Campbell and Yogo (2006) that the Bonferroni Q-test has important power advantages over the Bonferroni t-test. This study confirms acceptable finite-sample rejection rates when innovations are Gaussian and the assumptions of the Bonferroni Q-test are fulfilled. When the regressor is nonlocal-to-unity, however, the Q-test can over-reject the null in finite samples. Further, if innovations are modeled by a covariance nonstationarity approaching GARCH process, the right-tailed test again tends to over-reject the null of no predictability. The practical importance of this effect is demonstrated by GARCH parameter estimates based on S\&P500 returns. Previous evidence of predictability of the earnings-to-price ratio and dividend-to-price ratio has been replicated. Some doubt is however casted by the Monte Carlo evidence that finds over-rejection of the null for typical variance dynamics of real markets. Out-of-sample evidence, based on data emerged since the first publication of the method, is however eroding. In particular, both regressors are not found statistically significant at the 10\% level at the monthly as well as the quarterly sampling frequency.

@@

\begin{thebibliography}{}
\bibitem{} 
Campbell, J. Y., Yogo, M., 2005. Implementing the econometric methods in ‘‘Efficient tests of stock return
predictability’’. Unpublished working paper. University of Pennsylvania.
\bibitem{} 
Campbell, J. Y., Yogo, M., 2006. Efficient tests of stock return predictability. Journal of Financial Economics 81, 27-60.
\bibitem{} 
Elliott, G., Stock, J. H., 1994. Inference in time series regression when the order of integration of a regressor is
unknown. Econometric Theory 10, 672–700.
\bibitem{} 
Elliott, G., Rothenberg, T. J., Stock, J. H., 1996. Efficient Tests for an Autoregressive Unit Root. Econometrica 64(4), 813–836.
\bibitem{} 
Jacquier, E., Polson, N. G., Rossi, P. E., 2004. Bayesian analysis of stochastic volatility
models with fat-tails and correlated errors. J. Econometrics 122, 185–212.
\bibitem{} 
Cavaliere, G., 2004. Unit root tests under time-varying variances. Econometric Rev.
23, 259–292.
\bibitem{} 
Phillips, P. C. B., 1987. Towards a unified asymptotic theory for autoregression. Biometrika 74, 535–547.
\bibitem{} 
Phillips, P. C. B., 2014. On confidence Intervals for autoregressive roots and predictive regression. Econometrica 82(3), 1177-1195.
\bibitem{} 
Bollerslev, T., 1990. Modeling the coherence in short–run nominal exchange rates: a multivariate generalized ARCH model, Review of Economics and Statistics 73, 498–505.
\bibitem{} 
Engle, R. F., Kroner, K. F., 1995. Multivariate Simultaneous Generalized ARCH, Econometric Theory 11, 122–150.
\bibitem{} 
Glosten, L. R., Jagannathan, R., Runkle, D. E., 1993. On the relation between the expected value and the volatility of the nominal excess return on stocks. The Journal of Finance 48, 1779-1801.
\bibitem{} 
Stock, J. H., 1991. Confidence intervals for the largest autoregressive root in US macroeconomic time series.
Journal of Monetary Economics 28, 435–459.
\bibitem{} 
R Core Team, 2013. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL http://www.R-project.org/.
\bibitem{} 
Pfaff, B., 2008. Analysis of Integrated and Cointegrated Time Series with R. Second Edition. Springer, New York.

\end{thebibliography}

>>>>

Campbell and Yogo (2006) use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of nonstationarity can be rejected. Elliott and Stock (1994) show, however, that this does not guarantee valid inference via the t-statistic. Instead, Campbell and Yogo (2006) use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of Stock (1991). $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold for $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by Campbell and Yogo (2006), who use the DF-GLS test statistic proposed by Elliott et al. (1996) to construct the confidence interval for $c$. The application accompanying uses the closest tabulated values to the estimated values without interpolating.

@@

As argued by Phillips (2014), the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrate as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

It is therefore interesting to observe the behavior of the Bonferroni Q-test if innovations are modeled by a generalized autoregressive conditional heteroskedasticity [GARCH] process that approaches covariance nonstationarity. If the regressor is a valuation ratio, it seems sensible that there is a more or less stable correlation between the regressor and stock returns. A multivariate GARCH model that allows such a restriction is the Constant Conditional Correlations GARCH  [CCC-GARCH] model of Bollerslev (1990). It is defined as follows. Let $ \boldsymbol{z_{t}}$ be a bivariate standard normal random variable, i.e., $ \boldsymbol{z}_{t} \stackrel{i i d}{\sim} \mathrm{N}\left(\mathbf{0}, \boldsymbol{I}_{2}\right)$. Then the innovations are modeled as 

@@

\section{Empirical results}

@@

\subsection{Replication of empirical results from Campbell and Yogo (2006)}
Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of Campbell and Yogo (2006). The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. The regressors under consideration are the dividend-to-price ratio [ldp] and the earnings-to-price ratio [lep] where earnings, following Shiller (2000), are averaged over a moving 10-year period. Three different sampling frequencies, annual, quarterly, and monthly, are considered. Following Campbell and Yogo (2006), the confidence interval for $\beta$ is scaled by $\widehat{\sigma}_{e} / \widehat{\sigma}_{u}$ such that interpretation is made easier as the coefficient in equation $\ref{eqn:1}$ with unit variance innovations. Right-tailed tests with null hypothesis $H_0: \beta=0$ against alternative $H_1: \beta>0$ are considered where the null is rejected at 5\% significance level if the lower bound of $\beta$'s 90\% confidence interval is greater than zero. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by Campbell and Yogo (2006).  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. Thus the different selection is likely due to rounding errors. 

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor, invalidating inference based on t-statistics, which otherwise would be statistically significant. Based on the Bonferroni Q-test, the null hypothesis of no predictability can be rejected at the 5\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively, using data from Campbell and Yogo (2006). 
\subsection{Out-of-sample results}
Based on an extended dataset taken from Amid Goyal's website, only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First, returns in the extended dataset are of the S\&P500 instead of the CRSP value-weighted index. Also, due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since Campbell and Yogo (2006) use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos}, predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  

@@

Since the original publication of Campbell and Yogo (2006) a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 5\% significance level for any of the regressors and sampling frequencies considered. Both regressors are still highly persistent at all sampling frequencies, demonstrated by the confidence interval for $\rho$ containing unity in all cases. 
\begin{table}[h]
\small
\setlength\tabcolsep{5.3pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

The Bonferroni Q-test is an asymptotically valid test of predictability if the regressor's largest autoregressive root is local-to-unity and the innovations of regressor and regressand are bivariate Gaussian. It has been shown in the original work by Campbell and Yogo (2006) that the Bonferroni Q-test has important power advantages over the Bonferroni t-test. This study confirms acceptable finite-sample rejection rates when innovations are Gaussian and the assumptions of the Bonferroni Q-test are fulfilled. When the regressor is nonlocal-to-unity, however, the Q-test can over-reject the null in finite samples. Further, if innovations are modeled by a covariance nonstationarity approaching GARCH process, the right-tailed test again tends to over-reject the null of no predictability. The practical importance of this effect is demonstrated by GARCH parameter estimates based on S\&P500 returns. Previous evidence of predictability of the earnings-to-price ratio and dividend-to-price ratio has been replicated. Some doubt, however, is casted by the Monte Carlo evidence that finds over-rejection of the null for typical variance dynamics of real markets. Out-of-sample evidence, based on data emerged since the first publication of the method, is eroding. In particular, both regressors are not found statistically significant at the 5\% level at the monthly as well as the quarterly sampling frequency. In all cases, the pretest cannot reject the null of unacceptable size distortion of the t-test. Hence, inference based on the t-test is invalid.

@@

\begin{thebibliography}{}
\bibitem{} 
Campbell, J. Y., Yogo, M., 2005. Implementing the econometric methods in ‘‘Efficient tests of stock return
predictability’’. Unpublished working paper. University of Pennsylvania.
\bibitem{} 
Campbell, J. Y., Yogo, M., 2006. Efficient tests of stock return predictability. Journal of Financial Economics 81, 27-60.
\bibitem{} 
Elliott, G., Stock, J. H., 1994. Inference in time series regression when the order of integration of a regressor is
unknown. Econometric Theory 10, 672–700.
\bibitem{} 
Elliott, G., Rothenberg, T. J., Stock, J. H., 1996. Efficient Tests for an Autoregressive Unit Root. Econometrica 64(4), 813–836.
\bibitem{} 
Jacquier, E., Polson, N. G., Rossi, P. E., 2004. Bayesian analysis of stochastic volatility
models with fat-tails and correlated errors. J. Econometrics 122, 185–212.
\bibitem{} 
Cavaliere, G., 2004. Unit root tests under time-varying variances. Econometric Rev.
23, 259–292.
\bibitem{} 
Phillips, P. C. B., 1987. Towards a unified asymptotic theory for autoregression. Biometrika 74, 535–547.
\bibitem{} 
Phillips, P. C. B., 2014. On confidence Intervals for autoregressive roots and predictive regression. Econometrica 82(3), 1177-1195.
\bibitem{} 
Bollerslev, T., 1990. Modeling the coherence in short–run nominal exchange rates: a multivariate generalized ARCH model, Review of Economics and Statistics 73, 498–505.
\bibitem{} 
Engle, R. F., Kroner, K. F., 1995. Multivariate Simultaneous Generalized ARCH, Econometric Theory 11, 122–150.
\bibitem{} 
Glosten, L. R., Jagannathan, R., Runkle, D. E., 1993. On the relation between the expected value and the volatility of the nominal excess return on stocks. The Journal of Finance 48, 1779-1801.
\bibitem{} 
Stock, J. H., 1991. Confidence intervals for the largest autoregressive root in US macroeconomic time series.
Journal of Monetary Economics 28, 435–459.
\bibitem{} 
R Core Team, 2013. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL http://www.R-project.org/.
\bibitem{} 
Pfaff, B., 2008. Analysis of Integrated and Cointegrated Time Series with R. Second Edition. Springer, New York.
\bibitem{} 
Shiller, R.J., 2000. Irrational Exuberance. Princeton University Press, Princeton, NJ.
\end{thebibliography}
